Motion Planning and Robust Decentralized Fault-Tolerant Tracking Control of Hybrid UAVs and Biped Robots Team System for Search and Rescue Usage

### 2022-12-06 paper/paper.tex
Recise paper, IV, done

To the best of the authors' knowledge, most of the literature focus on only one specific problem in such an unmanned multi-agent S\&R system, such as task allocation problem, path planning problem or control problem. Additionally, few literatures illustrate the relationship between these problems. This leads us to propose a system architecture of hyibrid UAVs and biped robots team system (URTS) for S\&R usage. The flowchart of decision-making and control process of URTS is also given. We divide it into five main hierarchical processes, i.e., (i) task allocation, (ii) path planning, (iii) behavior layer, (iv) local motion planning and (v) tracking control. It is because the URTS needs to be able to assign different tasks to agents to perform first. After a task is assigned, if the task is to reach a goal location, a path to reach it needs to be planned. To make agent move on the path, a behavior corresponding to the environment is required to be determined. Then, a local motion corresponding to the behavior of the agent needs to be designed. Finally, a controller must be designed to track the trajectory of the motion. In order to further limit the scope of the study, we will focus on the latter two processes. But to illustrate how the whole system works, the first three problems are also briefly stated.

@@

\begin{figure*}[htbp]
    \centering
    \includegraphics[scale=.12]{fig/behavior.png}\caption{The structure of behavior layer. The leaves of the tree structure are the possible behaviors an agent can take. The behavior to be took at every moment will be decided in this block.}%
    \label{fig:behavior}
\end{figure*}

\subsection{Local Motion Planning}
After a specific behavior is determined, the next step is to design a motion to achieve the specific behavior. Local motion planning block is like path planning block but with smaller scale and higher resolution and precision. Collision checking is needed since we consider agent as a point in path planning block but it is a real mechanical body here. Furthermore, the kinodynamic constraint is handled in this block. Although motion planning and path planning are separated into two blocks, the technologies involved are similar and often with the same notion in other literature. Therefore, the output of this block is also a path $r[k]$. The flowchart of local motion planning block is shown in Fig. \ref{fig:LocalMotionPlanning}
\begin{figure*}[htbp]
    \centering
    \includegraphics[scale=.12]{fig/LMP.png}\caption{The flowchart of local motion planning. The corresponding motion planning will be executed according to the behavior determined by the behavior layer. The exception terminator in figure represents an exceptional condition that performs unconsidered behaviors. The reference path $r[k]$ is a sequence (or say a discrete signal) designed by a specific behavior block.}
    \label{fig:LocalMotionPlanning}
\end{figure*}

In Fig. \ref{fig:LocalMotionPlanning}, some basic behaviors of UAV and robot mentioned before are given to futher illustrate the flow of this block. To limit the scope of this article, we only focus on the motion planning of flying behavior of UAV and walking behavior of robot. They are belong to the moving behavior in Fig. \ref{fig:LocalMotionPlanning}. A more detailed description will be given in the next section.

@@

\section{system description of UAVs and biped robots in URTS}
In order to design a reference trajectory $r(t)$ for the motion of UAV and robot, their dynamic models must be given first. After the system description of UAV and robot in URTS, the motion planning of flying and walking as shown in Fig. \ref{fig:FandW} will be discussed subsequently and separately in the next two subsections.
\begin{figure*}[htbp]
    \centering
    \includegraphics[scale=.12]{fig/FandW.png}\caption{The flowchart of Flying and Walking. In both blocks, a smoothed path is obtained by post-processing first. Then the respective motion of behavior is designed. The final outputs of Flying and Walking are all desired reference path $r[k]$, but its value and dimension will vary according to the dimension of the system model.}
    \label{fig:FandW}
\end{figure*}
Before the discussion of the motion planning of these two behaviors, the following assumption is maded.
\textit{
    \begin{assumption} \label{asm:cc again}
        The space between obstacles is large enough to eliminate the need for collision checking again, and the average speed of agents is slow enough to ignore dynamic constraints
    \end{assumption}
}
However, for these two behaviors, there exists an inevitable kinematic constraint on the curvature of local motion. Although an accurate reference trajectory without breaking the curvature constraint can be designed, it is not easy to solve this problem. Additionally, it is not nessasry for these two behaviors in URTS since they are uesd to move from one location to another while the effect of error during moving caused by breaking the curvature constraint is relatively insignificant. At the same time, the \textit{Assumption \ref{asm:cc again}} makes sure the error will not cause collision. As an alternative, this problem can be handled by curve fitting which can be regarded as a post-process of the path $(\sigma_n)$. The post-process will appear in the begining of motion planning process of these two behaviors as shown in Fig. \ref{fig:FandW}.

\subsection{motion planning of flying of UAV}
A dynamic model about how the UAV moves in the physical world is given first. By Newton-Euler equation, the dynamic model of UAV can be formulated as \cite{sabatino2015quadrotor}:
\begin{equation} \label{eq:uav} 
    \begin{split}
        \begin{bmatrix}
            f_u \\ \tau_u
        \end{bmatrix}&=\begin{bmatrix}
            mI & 0 \\ 0 & J
        \end{bmatrix}\begin{bmatrix}
            \ddot{X} \\ \ddot{\Theta}
        \end{bmatrix}+\begin{bmatrix}
            0 \\ \dot{\Theta}\times(J\dot{\Theta})
        \end{bmatrix}+\begin{bmatrix}
            f_g \\ 0
        \end{bmatrix}
        \\
        &+\begin{bmatrix}
            K_F & 0 \\
            0 & K_\tau
        \end{bmatrix}\begin{bmatrix}
            \dot{X} \\ \dot{\Theta}
        \end{bmatrix}
        % Form 2 of rotation matrix R(\Theta)
        % &R(\Theta)=\begin{bmatrix*}[l]
        %     \cos\theta\cos\phi & \sin\phi\sin\theta\cos\psi-\cos\phi\sin\psi & R_1 \\
        %     \cos\theta\sin\phi & R_2 & R_3 \\
        %     -\sin\theta & \sin\phi\cos\theta & R_4
        % \end{bmatrix*}
        % \\
        % &R_1=\cos\phi\sin\theta\cos\psi+\sin\phi\sin\psi
        % \\
        % &R_2=\sin\phi\sin\theta\sin\psi+\cos\phi\cos\psi
        % \\
        % &R_3=\cos\phi\sin\theta\sin\psi-\sin\phi\cos\psi
        % \\
        % &R_4=\cos\phi\cos\theta
    \end{split}
\end{equation}
where $J=\begin{bmatrix}
    J_{x} & 0 & 0 \\
    0 & J_{y} & 0 \\
    0 & 0 & J_{z}
\end{bmatrix}$, $K_F=\begin{bmatrix}
    K_{x} & 0 & 0 \\
    0 & K_{y} & 0 \\
    0 & 0 & K_{z}
\end{bmatrix}$, $K_\tau=\begin{bmatrix}
    K_{\tau_x} & 0 & 0 \\
    0 & K_{\tau_y} & 0 \\
    0 & 0 & K_{\tau_z}
\end{bmatrix}$, $f_u =\begin{bmatrix}
    f_x \\ f_y \\ f_z
\end{bmatrix} = R(\Theta)\begin{bmatrix}
    0 \\ 0 \\ F
\end{bmatrix}$, $\tau_u=\begin{bmatrix}
    \tau_x \\ \tau_y \\ \tau_z
\end{bmatrix}$, $X=\begin{bmatrix}
    x \\ y \\ z
\end{bmatrix}$, $\Theta=\begin{bmatrix}
    \phi \\ \theta \\ \psi
\end{bmatrix}$, $f_g=\begin{bmatrix}
    0 \\ 0 \\ -mg
\end{bmatrix}$, $R(\Theta)=R_z(\psi)R_y(\theta)R_x(\phi)$, $R_z(\psi)=\begin{bmatrix} % form 1
    \cos\psi & -\sin\psi & 0 \\
    \sin\psi & \cos\psi & 0 \\
    0 & 0 & 1
\end{bmatrix}$, $R_y(\theta)=\begin{bmatrix}
    \cos\theta & 0 & \sin\theta \\
    0 & 1 & 0 \\
    -\sin\theta & 0 & \cos\theta
\end{bmatrix}$, $R_x(\phi)=\begin{bmatrix}
    1 & 0 & 0 \\
    0 & \cos\phi & -\sin\phi \\
    0 & \sin\phi & \cos\phi
\end{bmatrix}$.
% where $y'$ denotes the $y$ axis after rotating the $z$ axis and $x''$ denotes the $x$ axis after rotating the $y'$ axis
$g$ is the gravity acceleration, $m$ and $J$ are the mass and inertia matrix of UAV, respectively, $\tau_u$ and $F$ are the total torque and force acting on UAV, respectively, $\Theta$ is the Euler angles in body frame, $X$ is the postion of center of mass (CoM) in inertial frame, $K_\tau$ and $K_F$ are the aerodynamic damping coefficients, and $R(\Theta)$ is the intrinsic rotation matrix from body frame to inertial frame. This model treats the UAV as a mass point and can control the total force $F$ and the total torque $\tau_u$. For UAV, the reference trajectory $r(t)=[x_r(t),y_r(t),z_r(t),\phi_r(t),\theta_r(t),\psi_r(t)]^T\in\mathbb{R}^{6}$ is in the task space, where the subscript $r$ denotes the reference.

\textit{
    \begin{remark}
        Since the quadrotor has four rotors, we only have four control input. To simplify the model, the UAV (quadrotor) dynamic model in (\ref{eq:uav}) considers $u'(t)=[F, \tau_u^T]^T=[F, \tau_x, \tau_y, \tau_z]^T$ as the equivalent control input for the four rotors. Besides, since $u'(t)\in\mathbb{R}^4$ has two less degrees of freedom than $r(t)\in\mathbb{R}^6$, UAV is an underactuated system.
    \end{remark}
}

Now, suppose the UAV flying occurs between time step $t_1$ and $t_2$, that is, $\beta_n=\mathit{flying}, n\in\mathbb{Z}\cap[t_1,t_2]$. The corresponding path $(\sigma_n), n\in\mathbb{Z}\cap[t_1,t_2]$ will be smoothed first by linear interpolation and then by cubic spline interpolation, which gives the smoothed path $(\sigma_n'), n\in\mathbb{Z}\cap[t_1,t_1+D(t_2-t_1)], \sigma_n'\in\mathbb{R}^3$, where $D\in\mathbb{Z}^+$ is the interpolation density. Then, $(\sigma_n')$ will be the position reference path $[
    x_r[k], y_r[k], z_r[k]
]^T$. Subsequently, the orientation reference path, row angle $\phi_r[k]$, pitch angle $\theta_r[k]$ and yaw angle $\psi_r[k]$ are all considered. $\phi_r[k]$ is set to zero since no need for spinning when flying. $\theta_r[k]$ and $\psi_r[k]$ cannot be set beforehand since UAV is an underactuated system, which will be discussed in the next section. Finally, the reference path $r[k]$ of UAV can be obtained by combining them together, i.e., $r[k] = [
    x_r[k], y_r[k], z_r[k], \psi_r[k]
]^T\in\mathbb{R}^{4}$. The flowchart is shown in Fig. \ref{fig:FandW}.

@@

\subsection{motion of walking of robot}
By Lagrange equation, the dynamic model of biped robot can be formulated as:
\begin{equation} \label{eq:robot} 
    \begin{split}
        & \tau_R = M_R(q)\ddot{q} + C(q,\dot{q})\dot{q} + G(q)    
    \end{split}
\end{equation}
where $\tau_R$ is the total torque on revolute joints, $q,\dot{q},\ddot{q}\in\mathbb{R}^{12}$  are angular position, angular velocity, and angular acceleration vector of revolute joints, $M_R(q)\in\mathbb{R}^{12\times 12}$ is the inertia matrix, $C(q,\dot{q})\in\mathbb{R}^{12}$ is the Coriolis and centripetal force vector and $G(q)\in\mathbb{R}^{12}$ is the gravitational force vector. The detailed kinematic and dynamic parameters can be found in the online source \cite{ourrobot}. For robot, the reference trajectory $r(t)=q_r(t)\in\mathbb{R}^{12}$ is in the joint space. Furthermore, the walking of biped robot suffers from the falling problem, i.e, how to find a stable walking pattern to prevent robot from falling. These make the design of walking motion more difficult. In this paper, a three-dimensional linear inverted pendulum Model (3D-LIPM) \cite{kajita2001real} is used to design the walking motion.

With 3D-LIPM, we can significantly reduce the amount of computation. Let us define the body frame of robot as $\{ \widehat{X_b}, \widehat{Y_b}, \widehat{Z_b} \}$ as in \cite{ourrobot}. Taking the forward direction of robot as $\widehat{X_b}$ direction, the left direction as $\widehat{Y_b}$ direction, and the torso direction as $\widehat{Z_b}$ direction in body frame, "Falling" means the moments on the robot in $\widehat{X_b}$ and $\widehat{Y_b}$ direction are not zero. More accuately, the robot will not fall if the zero moment point (ZMP) lies in the support polygon, i.e., the convex hull of face of supported foots. The ZMP in $\widehat{X_b}$ direction can be discribed as \cite{huang2001planning} (The ZMP in $\widehat{Y_b}$ direction as the same form):
\begin{equation} \label{eq:x_zmp}
    x_{zmp} = \frac{\sum_{i=1}^{12} (m_i(\ddot{z}_i+g)x_i - m_i\ddot{x}_iz_i - I_{iy}\ddot{\Omega}_{iy})}
                   {\sum_{i=1}^{12} m_i(\ddot{z}_i+g)}
\end{equation}
where $m_i$ is the CoM, $x_i, z_i$ are the linear position components, $I_{iy}$ is the inertial component, and $\ddot{\Omega}_{iy}$ is the angular velocity component of link $i$. However, it is difficult to directly calculate the analytical solution of $q_r(t)$ through (\ref{eq:x_zmp}). Since there is a complex coordinate transformation between $q_r(t)$ and $x_i, z_i, \ddot{\Omega}_{iy}$. At the same time, it is necessary to ensure that $x_{zmp}$ falls on the support polygon but the support polygon also has a relationship with $q_r(t)$. To simplify this complex problem, an approximate solution can be derived through 3D-LIPM. It is to find CoM reference first and then obtain $q_r(t)$ by using inverse kinematic (IK) with given step size, step height, step period and CoM height. Many researchers have used this method to avoid complex calculations for ZMP of actual robot dynamic model. Although there exist a model error between the actual dynamic model and 3D-LIPM, the design process will be more simple. The overall process is shown in Fig. \ref{fig:FandW}.
% \begin{figure}[htbp]
%     \centering
%     \includegraphics[scale=.3]{fig/walking.pdf}\caption{flowchart of biped robot walking}%
%     \label{fig:walking}
% \end{figure}

Following the same step in UAV, the smoothed path $(\sigma_n')$ for robot can be obtained at first. For the convenience of explanation, suppose walking is occured between time step $1$ and $N$, i.e., $n\in\mathbb{Z}\cap[1,N]$. Note that $(\sigma_n')$ is not actual CoM reference in robot case since CoM of robot need to "swinging" for balance. Despite that, $(\sigma_n')$ tells the robot the position to go so the $\widehat{X_b}$ direction can be obtained by doing finite difference on $(\sigma_n')$ due to the expectation that the robot will move forward (rather than sideways or backward). To keep torso upright, the $\widehat{Z_b}$ direction is equal to the $z$-axis in the inertial frame $\widehat{Z_g}$. Given $\widehat{X_b}$ and $\widehat{Z_b}$, $\widehat{Y_b}$ can be obtained obviously through cross product. The sequence of body frame, i.e., CoM orientation path $(CO_n)$ can be obtained through the above steps.

\textit{
    \begin{remark}
        A frame in $\mathbb{R}^3$ can be determined by giving the "position" and "orientation" with respect to a reference frame. That is, given the position and orientation of two joints in a link with known kinematics, the position and orientation of joints between them can be found by IK. Hence, we need to find the  position path and orientation path, which compose the desired path.
    \end{remark}
}

Let us denote the $x$ and $y$ component of $\sigma_n'$ in $(\sigma_n')$ as the sequence $(\sigma^{1}_{n}), \sigma^{1}_{n}\in\mathbb{R}^2$. The left and right "envelopes", $(\sigma^{2}_{n})$ and $(\sigma^{3}_{n})$, of $(\sigma^{1}_{n})$ with a fixed distance $L_1$ can be found by $(\sigma^{1}_{n})$ and $(CO_n)$ through the geometric relation between $(\sigma^{i}_{n}), i=1,2,3$, where $L_1$ is feet width (or shoulder width). Then the $x$ and $y$ component of left and right foothold paths, $(\sigma^{2}_{k_n})$ and $(\sigma^{3}_{k_n})$, can be obtained by a given step size, which are the subsequence of $(\sigma^{2}_{n})$ and $(\sigma^{3}_{n})$, respectively. Finally, left and right foothold paths $(\sigma^{i}_{k_n}), \sigma^{i}_{k_n}\in\mathbb{R}^3, i=4,5$ are found by adding $z$ component which is given by ground height.

After foothold paths are obtained, ankle position path can also be obtained by the given step height which is customized by the designer or based on the height of the obstacle to be crossed. Taking the left foothold path as an example, $x$ and $y$ component of the highest position of ankle during stride are set as middle point of two footholds $\sigma^{2}_{k_m}$ and $\sigma^{2}_{k_{m+1}}$ where $m\in\mathbb{Z}\cap[1,N-1]$, and the $z$ component is given by step height. By using cubic spline interpolation, we have the left and right ankle position paths, $(\sigma^{6}_{n})$ and $(\sigma^{7}_{n})$. The ankle orientation path is found by the gradient of ground. Finally, the left and right ankle paths, $(\sigma^{8}_{n})$ and $(\sigma^{9}_{n})$, are found by combining the position and orientation path together. So far, the remaining work is to find out the CoM path and then to combine with the ankle path to calculate the joint path through IK.

>>>>

To the best of the authors' knowledge, most of the literature focus on only one specific problem in such an unmanned multi-agent S\&R system, such as task allocation problem, path planning problem or control problem. Additionally, few literatures illustrate the relationship between these problems. This leads us to propose a system architecture of hybrid UAVs and biped robots team system (URTS) for S\&R usage. The flowchart of decision-making and control process of URTS is also given. We divide it into five main hierarchical processes, i.e., (i) task allocation, (ii) path planning, (iii) behavior layer, (iv) local motion planning and (v) tracking control. It is because the URTS needs to be able to assign different tasks to agents to perform first. After a task is assigned, if the task is to reach a goal location, a path to reach it needs to be planned. To make agent move on the path, a behavior corresponding to the environment is required to be determined. Then, a local motion corresponding to the behavior of the agent needs to be designed. Finally, a controller must be designed to track the trajectory of the motion. In order to further limit the scope of the study, we will focus on the latter two processes. But to illustrate how the whole system works, the first three problems are also briefly stated.

@@

\begin{figure*}[htbp]
    \centering
    \includegraphics[scale=.12]{fig/behavior.png}\caption{The structure of behavior layer. (a) The behavior set of each agent in URTS. The leaves of the tree structure are the possible behaviors an agent can take. The behavior to be took at every moment by each agent will be decided in this block. For UAVs, the moving behavior set is predefined in (b). For robots, the moving behavior set is predefined in (c). (b) The moving behavior set of each UAV. (c) The moving behavior set of each robot.}%
    \label{fig:behavior}
\end{figure*}

\subsection{Local Motion Planning}
After a specific behavior is determined, the next step is to design a motion to achieve the specific behavior. Local motion planning block is like path planning block but with smaller scale and higher resolution and precision. Collision checking is needed since we consider agent as a point in path planning block but it is a real mechanical body here. Furthermore, the kinodynamic constraint is handled in this block. Although motion planning and path planning are separated into two blocks, the technologies involved are similar and often with the same notion in other literature. Therefore, the output of this block is also a path $r[k]$. The flowchart of local motion planning block is shown in Fig. \ref{fig:LMP}
\begin{figure*}[htbp]
    \centering
    \includegraphics[scale=.12]{fig/LMP.png}\caption{The flowchart of local motion planning. (a) The local motion planning of each agent in URTS . The corresponding motion planning of an agent will be executed according to the behavior determined by the behavior layer. The exception terminator in figure represents an exceptional condition that performs unconsidered behaviors. The reference path $r[k]$ is a sequence (or say a discrete signal) designed by a specific behavior block. For UAVs, the moving block is predefined in (b). For robots, the moving block is predefined in (c). (b) The moving block of each UAV where the flying block is predefined in \ref{fig:FandW} (c) The moving block of each robot where the walking block is predefined in \ref{fig:FandW}}
    \label{fig:LMP}
\end{figure*}

In Fig. \ref{fig:LMP}, some basic behaviors of UAV and robot mentioned before are given to futher illustrate the flow of this block. To limit the scope of this article, we only focus on the motion planning of flying behavior of UAV and walking behavior of robot. They are belong to the moving behavior in Fig. \ref{fig:LMP}. A more detailed description will be given in the next section.

@@

\section{system description of UAVs and biped robots in URTS}
In order to design a reference trajectory $r(t)$ for the motion of UAV and robot in URTS, their dynamic models must be given first. After the system description of UAV and robot in URTS, the motion planning of flying and walking as shown in Fig. \ref{fig:FandW} will be discussed subsequently and separately in the next two subsections.
\begin{figure*}[htbp]
    \centering
    \includegraphics[scale=.12]{fig/FandW.png}\caption{The flowchart of flying block and walking block in \ref{fig:LMP}. In both blocks, a smoothed path is obtained by post-processing first. Then the respective motion of behavior is designed.
    %The final outputs of flying block and walking block are all desired reference path $r[k]$, but its value and dimension will vary according to the dimension of the system model.
    (a) The flying block of each UAV. By combining the position path $(\sigma'_n)$ and setting $\phi_d=0$ (let UAV fly without spinning), we have the reference path $r[k]$.
    (b) The walking block of each robot. Follow the process in Section IV-B, we have the reference path $r[k]$.}
    \label{fig:FandW}
\end{figure*}
Before the discussion of the motion planning of these two behaviors, the following assumption is maded.
\textit{
    \begin{assumption} \label{asm:cc again}
        The space between obstacles is large enough to eliminate the need for collision checking again, and the average speed of agents is slow enough to ignore dynamic constraints
    \end{assumption}
}
However, for these two behaviors, there exists an inevitable kinematic constraint on the curvature of local motion. Although an accurate reference trajectory without breaking the curvature constraint can be designed, it is not easy to solve this problem. Additionally, it is not nessasry for these two behaviors in URTS since they are uesd to move from one location to another while the effect of error during moving caused by breaking the curvature constraint is relatively insignificant. At the same time, the \textit{Assumption \ref{asm:cc again}} makes sure the error will not cause collision. As an alternative, this problem can be handled by curve fitting which can be regarded as a post-process of the path $(\sigma_n)$. The post-process will appear in the begining of motion planning process of these two behaviors as shown in Fig. \ref{fig:FandW}.

\subsection{motion planning of flying of UAV}
A dynamic model about how an UAV in URTS moves in the physical world is given first. By Newton-Euler equation, the dynamic model of each UAV in URTS can be formulated as \cite{sabatino2015quadrotor}:
\begin{equation} \label{eq:uav} 
    \begin{split}
        \begin{bmatrix}
            f_u \\ \tau_u
        \end{bmatrix}&=\begin{bmatrix}
            mI & 0 \\ 0 & J
        \end{bmatrix}\begin{bmatrix}
            \ddot{X} \\ \ddot{\Theta}
        \end{bmatrix}+\begin{bmatrix}
            0 \\ \dot{\Theta}\times(J\dot{\Theta})
        \end{bmatrix}+\begin{bmatrix}
            f_g \\ 0
        \end{bmatrix}
        \\
        &+\begin{bmatrix}
            K_F & 0 \\
            0 & K_\tau
        \end{bmatrix}\begin{bmatrix}
            \dot{X} \\ \dot{\Theta}
        \end{bmatrix}
        % Form 2 of rotation matrix R(\Theta)
        % &R(\Theta)=\begin{bmatrix*}[l]
        %     \cos\theta\cos\phi & \sin\phi\sin\theta\cos\psi-\cos\phi\sin\psi & R_1 \\
        %     \cos\theta\sin\phi & R_2 & R_3 \\
        %     -\sin\theta & \sin\phi\cos\theta & R_4
        % \end{bmatrix*}
        % \\
        % &R_1=\cos\phi\sin\theta\cos\psi+\sin\phi\sin\psi
        % \\
        % &R_2=\sin\phi\sin\theta\sin\psi+\cos\phi\cos\psi
        % \\
        % &R_3=\cos\phi\sin\theta\sin\psi-\sin\phi\cos\psi
        % \\
        % &R_4=\cos\phi\cos\theta
    \end{split}
\end{equation}
where $J=\begin{bmatrix}
    J_{x} & 0 & 0 \\
    0 & J_{y} & 0 \\
    0 & 0 & J_{z}
\end{bmatrix}$, $K_F=\begin{bmatrix}
    K_{x} & 0 & 0 \\
    0 & K_{y} & 0 \\
    0 & 0 & K_{z}
\end{bmatrix}$, $K_\tau=\begin{bmatrix}
    K_{\tau_x} & 0 & 0 \\
    0 & K_{\tau_y} & 0 \\
    0 & 0 & K_{\tau_z}
\end{bmatrix}$, $f_u =\begin{bmatrix}
    f_x \\ f_y \\ f_z
\end{bmatrix} = R(\Theta)\begin{bmatrix}
    0 \\ 0 \\ F
\end{bmatrix}$, $\tau_u=\begin{bmatrix}
    \tau_x \\ \tau_y \\ \tau_z
\end{bmatrix}$, $X=\begin{bmatrix}
    x \\ y \\ z
\end{bmatrix}$, $\Theta=\begin{bmatrix}
    \phi \\ \theta \\ \psi
\end{bmatrix}$, $f_g=\begin{bmatrix}
    0 \\ 0 \\ -mg
\end{bmatrix}$, $R(\Theta)=R_z(\psi)R_y(\theta)R_x(\phi)$, $R_z(\psi)=\begin{bmatrix} % form 1
    \cos\psi & -\sin\psi & 0 \\
    \sin\psi & \cos\psi & 0 \\
    0 & 0 & 1
\end{bmatrix}$, $R_y(\theta)=\begin{bmatrix}
    \cos\theta & 0 & \sin\theta \\
    0 & 1 & 0 \\
    -\sin\theta & 0 & \cos\theta
\end{bmatrix}$, $R_x(\phi)=\begin{bmatrix}
    1 & 0 & 0 \\
    0 & \cos\phi & -\sin\phi \\
    0 & \sin\phi & \cos\phi
\end{bmatrix}$.
% where $y'$ denotes the $y$ axis after rotating the $z$ axis and $x''$ denotes the $x$ axis after rotating the $y'$ axis
$g$ is the gravity acceleration, $m$ and $J$ are the mass and inertia matrix of UAV, respectively, $\tau_u$ and $F$ are the total torque and force acting on UAV, respectively, $\Theta$ is the Euler angles in body frame, $X$ is the postion of center of mass (CoM) in inertial frame, $K_\tau$ and $K_F$ are the aerodynamic damping coefficients, and $R(\Theta)$ is the intrinsic rotation matrix from body frame to inertial frame. This model treats the UAV as a mass point and can control the total force $F$ and the total torque $\tau_u$. For UAV, the reference trajectory $r(t)=[x_r(t),y_r(t),z_r(t),\phi_r(t),\theta_r(t),\psi_r(t)]^T\in\mathbb{R}^{6}$ is in the task space, where the subscript $r$ denotes the reference.

\textit{
    \begin{remark}
        Since the UAV (quadrotor) has four rotors, we only have four control input. To simplify the model, the UAV dynamic model in (\ref{eq:uav}) considers the actuator control input $u'(t)=[F, \tau_u^T]^T=[F, \tau_x, \tau_y, \tau_z]^T$ as the equivalent control input for the four rotors. Besides, since $u'(t)\in\mathbb{R}^4$ has two less degrees of freedom than $r(t)\in\mathbb{R}^6$, UAV is an underactuated system. This makes the two degrees of freedom in the reference trajectory of UAV cannot be assigned arbitrarily but be reversed from the dynamic equation in (\ref{eq:uav}).
    \end{remark}
}

Now, suppose the UAV flying behavior occurs between time step $t_1$ and $t_2$, that is, $\beta_n=\mathit{flying}, n\in\mathbb{Z}\cap[t_1,t_2]$. The corresponding path $(\sigma_n), n\in\mathbb{Z}\cap[t_1,t_2]$ will be smoothed first by linear interpolation and then by cubic spline interpolation, which gives the smoothed path $(\sigma_n'), n\in\mathbb{Z}\cap[t_1,t_1+D(t_2-t_1)], \sigma_n'\in\mathbb{R}^3$, where $D\in\mathbb{Z}^+$ is the interpolation density. Then, $(\sigma_n')$ will be the position reference path $[
    x_r[k], y_r[k], z_r[k]
]^T$. Subsequently, the orientation reference path, row angle $\phi_r[k]$, pitch angle $\theta_r[k]$ and yaw angle $\psi_r[k]$ are all considered. $\phi_r[k]$ is set to zero since no need for spinning when flying. $\theta_r[k]$ and $\psi_r[k]$ cannot be set beforehand since UAV is an underactuated system, which will be discussed in the next section. Finally, the reference path $r[k]$ of UAV can be obtained by combining them together, i.e., $r[k] = [
    x_r[k], y_r[k], z_r[k], \psi_r[k]
]^T\in\mathbb{R}^{4}$. The flowchart is shown in Fig. \ref{fig:FandW}.

@@

\subsection{motion of walking of robot}
By Lagrange equation, the dynamic model of a biped robot in URTS can be formulated as:
\begin{equation} \label{eq:robot} 
    \begin{split}
        & \tau_R = M_R(q)\ddot{q} + C(q,\dot{q})\dot{q} + G(q)    
    \end{split}
\end{equation}
where $\tau_R$ is the total torque on revolute joints, $q,\dot{q},\ddot{q}\in\mathbb{R}^{12}$  are angular position, angular velocity, and angular acceleration vector of revolute joints, $M_R(q)\in\mathbb{R}^{12\times 12}$ is the inertia matrix, $C(q,\dot{q})\in\mathbb{R}^{12}$ is the Coriolis and centripetal force vector and $G(q)\in\mathbb{R}^{12}$ is the gravitational force vector. The detailed kinematic and dynamic parameters can be found in the online source \cite{ourrobot}. For biped robot, the reference trajectory $r(t)=q_r(t)\in\mathbb{R}^{12}$ is in the joint space. Furthermore, the walking of biped robot suffers from the falling problem, i.e, how to find a stable walking pattern to prevent robot from falling. These make the design of walking motion more difficult. In this paper, a three-dimensional linear inverted pendulum Model (3D-LIPM) \cite{kajita2001real} is used to design the walking motion of each biped robot in URTS.

With 3D-LIPM, we can significantly reduce the amount of computation. Let us define the body frame of biped robot as $\{ \widehat{X_b}, \widehat{Y_b}, \widehat{Z_b} \}$ as in \cite{ourrobot}. Taking the forward direction of biped robot as $\widehat{X_b}$ direction, the left direction as $\widehat{Y_b}$ direction, and the torso direction as $\widehat{Z_b}$ direction in body frame, "Falling" means the moments on the robot in $\widehat{X_b}$ and $\widehat{Y_b}$ direction are not zero. More accuately, the biped robot will not fall if the zero moment point (ZMP) lies in the support polygon, i.e., the convex hull of face of supported foots. The ZMP in $\widehat{X_b}$ direction can be discribed as \cite{huang2001planning} (The ZMP in the $\widehat{Y_b}$ direction is the same form):
\begin{equation} \label{eq:x_zmp}
    x_{zmp} = \frac{\sum_{i=1}^{12} (m_i(\ddot{z}_i+g)x_i - m_i\ddot{x}_iz_i - I_{iy}\ddot{\Omega}_{iy})}
                   {\sum_{i=1}^{12} m_i(\ddot{z}_i+g)}
\end{equation}
where $m_i$ is the CoM, $x_i, z_i$ are the linear position components, $I_{iy}$ is the inertial component, and $\ddot{\Omega}_{iy}$ is the angular acceleration component of link $i$. However, it is difficult to directly calculate the analytical solution of $q_r(t)$ through (\ref{eq:x_zmp}). Since there exists a complex coordinate transformation between $q_r(t)$ and $x_i, z_i, \ddot{\Omega}_{iy}$. At the same time, it is necessary to ensure that $x_{zmp}$ falls in the support polygon which also has a relationship with $q_r(t)$. To simplify this complex problem, an approximate solution can be derived through 3D-LIPM. We find CoM reference first and then obtain $q_r(t)$ by using inverse kinematic (IK) with given step size, step height, step period and CoM height. Many researchers have used this method to avoid complex calculations for ZMP of the actual robot dynamic model. Although there exists a model error between the actual dynamic model and 3D-LIPM, the design process will be more simple. The overall process is shown in Fig. \ref{fig:FandW}.
% \begin{figure}[htbp]
%     \centering
%     \includegraphics[scale=.3]{fig/walking.pdf}\caption{flowchart of biped robot walking}%
%     \label{fig:walking}
% \end{figure}

Following the same step in UAV, the smoothed path $(\sigma_n')$ for biped robot can be obtained at first. For the convenience of explanation, suppose walking is occured between time step $1$ and $N$, i.e., $n\in\mathbb{Z}\cap[1,N]$. Note that $(\sigma_n')$ is not actual CoM reference in robot case since CoM of robot need to "swinging" for balance. Despite of that, $(\sigma_n')$ tells the biped robot the position to go so the $\widehat{X_b}$ direction can be obtained by doing finite difference on $(\sigma_n')$ due to the expectation that the biped robot will move forward (rather than sideways or backward). To keep torso upright, the $\widehat{Z_b}$ direction is equal to the $z$-axis in the inertial frame $\widehat{Z_g}$. Given $\widehat{X_b}$ and $\widehat{Z_b}$, $\widehat{Y_b}$ can be obtained obviously through cross product. The sequence of body frame, i.e., CoM orientation path $(CO_n)$ can be obtained through the above steps.

\textit{
    \begin{remark}
        A frame in $\mathbb{R}^3$ can be determined by giving the "position" and "orientation" with respect to a reference frame. That is, given the position and orientation of two joints in a link with known kinematics, the position and orientation of joints between them can be found by \textnormal{IK}. Hence, we need to find the  position path and orientation path, which compose the desired path.
    \end{remark}
}

Let us denote the $x$ and $y$ component of $\sigma_n'$ in $(\sigma_n')$ as the sequence $(\sigma^{1}_{n}), \sigma^{1}_{n}\in\mathbb{R}^2$. The left and right "envelopes", $(\sigma^{2}_{n})$ and $(\sigma^{3}_{n})$, of $(\sigma^{1}_{n})$ with a fixed distance $L_1$ can be found by $(\sigma^{1}_{n})$ and $(CO_n)$ through the geometric relation among $(\sigma^{i}_{n}), i=1,2,3$, where $L_1$ is the feet width (or shoulder width). Then the $x$ and $y$ component of the left and right foothold paths, $(\sigma^{2}_{k_n})$ and $(\sigma^{3}_{k_n})$, can be obtained by a given step size, which are the subsequence of $(\sigma^{2}_{n})$ and $(\sigma^{3}_{n})$, respectively. Finally, the left and right foothold paths $(\sigma^{i}_{k_n}), \sigma^{i}_{k_n}\in\mathbb{R}^3, i=4,5$ are found by adding the $z$ component which is given by ground height.

After foothold paths are obtained, ankle position path can also be obtained by the given step height which is customized by the designer or based on the height of the obstacle to be crossed. Taking the left foothold path as an example, $x$ and $y$ component of the highest position of ankle during stride are set as the middle point of two footholds $\sigma^{2}_{k_m}$ and $\sigma^{2}_{k_{m+1}}$ where $m\in\mathbb{Z}\cap[1,N-1]$, and the $z$ component is given by the step height. By using the cubic spline interpolation, we have the left and right ankle position paths, $(\sigma^{6}_{n})$ and $(\sigma^{7}_{n})$. The ankle orientation path is found by the gradient of ground. Finally, the left and right ankle paths, $(\sigma^{8}_{n})$ and $(\sigma^{9}_{n})$, are found by combining the position and orientation path together. So far, the remaining work is to find out the CoM path and then to combine with the ankle path to calculate the joint path through IK.
